\documentclass[10pt]{article}
\usepackage{graphicx}
\usepackage{titletoc, tocloft}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{color}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{etoolbox}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{pgf-pie}
\usepackage{fontawesome5}
\usepackage{pgfplots}
\pgfplotsset{compat=newest} 
\usepackage{pgfplotstable}
\usepackage{float}
\pgfplotsset{compat=1.17}
\usepackage{subcaption}
\usetikzlibrary{arrows, positioning, shadows}
\setlength{\cftsecnumwidth}{3.5em}
\makeatletter
\patchcmd{\l@section}
    {\cftsecfont #1}
    {\cftsecfont {#1}}
    {}
    {}
\makeatother
\renewcommand\cftsecfont{\bf\MakeUppercase} 
\renewcommand\thesection{\Roman{section}}
\usepackage{titlesec}
\titleformat{\section}
  {\large\bf\scshape}{\thesection}{0.2in}{}
\usepackage{tcolorbox}
\usepackage{fancybox}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{multicol}
\usepackage{tipa}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{tikz-qtree-compat}
  \usetikzlibrary{arrows.meta}
    \tikzset{every tree node/.style={align=center,anchor=north}}
    \usetikzlibrary{fit}
%\usepackage{fancyhdr}
\pagestyle{empty}
%\rhead{TULCON17, University of toronto}
%\lhead{9/3/2024}
%\fancyhfoffset{0in}
\usepackage[utf8]{inputenc}
\usepackage[top=0.4in, bottom=0.4in, left=0.4in, right=0.4in]{geometry}
\usepackage{slantsc}
\usepackage{bold-extra}
\usepackage{amsfonts}
\usepackage{blindtext}
\usepackage{booktabs}
\usepackage{multicol}
\setlength{\parindent}{0pt} 
\usepackage{linguex}
\usepackage{gb4e}
\usepackage[symbol]{footmisc}
\usepackage{hyperref}
\definecolor{pastelgreen}{RGB}{193, 225, 193}
\definecolor{peach}{RGB}{255, 229, 180}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
 		\definecolor{camouflagegreen}{rgb}{0.47, 0.53, 0.42}
   \definecolor{darkcyan}{rgb}{0.0, 0.55, 0.55}
\hypersetup{
    colorlinks=true,
    linkcolor=purple,
    citecolor=camouflagegreen,
    urlcolor=darkcyan,
    }
\newcommand{\myframe}[2]{
    \begin{tcolorbox}[colback=white,colframe=black,sharp corners, title={#1}]
        #2
    \end{tcolorbox}
}
\begin{document}

%TC:ignore 
\setstretch{1.0} 
\begin{center}
   \Large{\textsc{\textbf{Nikola Moore}}}\\
   \normalsize \faEnvelope\ \href{mailto:nowe.moore@gmail.com}{nowe.moore@gmail.com} $\mid$ \faPhone\ +44 749 221 0683 $\mid$ \faLink\ \href{nowemoore.com}{nowemoore.com} $\mid$ \faLinkedin\ \href{https://www.linkedin.com/in/nowemoore/}{LinkedIn} $\mid$ \faMapMarker\ London, UK
\end{center}
\noindent\colorbox{black}{\parbox{\textwidth}{\color{white}\textbf{\faGraduationCap\ Education}}}
Philadelphia, Pennsylvania  \hfill 08/2021 - 05/2025\\
\textbf{University of Pennsylvania, \textit{Cum Laude Honours BA and Research MA}.}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt,
topsep=0pt,
itemsep=0pt]
\item Linguistics (MA); Cognitive Science (computation \& cognition) \& Linguistics (BA). Minor: Computer Science.
\item Activities: Penn Linguistics Society (President), Effective Altruism (Fellow), PLC49 Finance Committee (Jr Member, managed a budget of \$20,000), 2+ years of graduate research experience (Cognitive Science, LLMs).
\end{itemize}
\vspace{0.1in}
Cambridge, UK \hfill									09/2023 - 06/2024\\
\textbf{Pembroke College, University of Cambridge, \textit{visiting student.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt,
topsep=0pt,
itemsep=0pt]
\item Final mark: first-class; two independent studies (experimental quantitative and qualitative data analysis).
\item Activities: STEM Smart Mentoring (mentor), Parmee Prize for Entrepreneurship (finalist).
\end{itemize}
\vspace{0.1in}
Bratislava, Slovakia \hfill									08/2017 – 06/2021\\
\textbf{LEAF Academy, \textit{US HS Diploma.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt,
topsep=0pt,
itemsep=0pt]
\item	Entrepreneurship (design thinking, business models, resource allocation), AP\textsuperscript{\scriptsize \textregistered} Scholar w. Distinction.
\end{itemize}
\vspace{0.1in}
\textbf{Other Programmes \& Qualifications:} Google Data Analytics Certificate (in progress), AI Alignment (BlueDot Impact, 2024), ESPR (2019), Global Challenges Project Boston (2025).\\

\noindent\colorbox{black}{\parbox{\textwidth}{\color{white}\textbf{\faCogs\ Relevant Projects \& Experience}}}
Seattle, WA, USA \hfill 02/2024 – 06/2025\\
\textbf{Code.org, \textit{intern.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt, topsep=0pt, itemsep=0pt]
\item Implemented an intl. PD curriculum as a user-friendly async course, used by 30+ participants.
\end{itemize}
\vspace{0.1in}
Philadelphia, PA, USA \hfill 07/2024 – 04/2025\\
\textbf{The New Mind workshop series + AI4GOOD Ideathon, \textit{lead.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt, topsep=0pt, itemsep=0pt]
\item Hand-designed, branded, and hosted guest-speaker workshop series + ideathon on AI safety; trained 120+ participants, managed a budget of \$14,000.
\end{itemize}
\vspace{0.1in}
Philadelphia, PA, USA \hfill 12/2024 – 05/2025\\
\textbf{Department of Linguistics, University of Pennsylvania, \textit{undergraduate teaching assistant.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt, topsep=0pt, itemsep=0pt]
\item Adapted 30+ problem sets to a more accessible format, fostered active learning in a class of 65+ students.
\end{itemize}
\vspace{0.1in}
Philadelphia, PA, USA \hfill 12/2021 – 12/2024\\
\textbf{Weingarten Center, University of Pennsylvania, \textit{tutor.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt, topsep=0pt, itemsep=0pt]
\item Tutored students and groups online and in-person, helped run revision study halls during reading days.
\end{itemize}
\vspace{0.1in}
Cambridge, UK \hfill 07/2023 – 08/2023\\
\textbf{Summer Research Programme by CSI, \textit{participant.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt, topsep=0pt, itemsep=0pt]
\item Completed a 3-week taught programme, delivered a research project on tech application across state institutions.
\end{itemize}
\vspace{0.1in}
Gashora, Rwanda \hfill 05/2022 – 07/2022\\
\textbf{Gashora Girls Academy of Science and Technology, \textit{teaching fellow.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt, topsep=0pt, itemsep=0pt]
\item Designed a term worth of curriculum for two cohorts and contributed to residential life (dining and college advice).
\end{itemize}
\vspace{0.1in}
Bratislava, Slovakia \hfill 05/2022 – 08/2022\\
\textbf{The Ministry of Finance, \textit{project management intern.}}
\begin{itemize}[label=$\blacktriangleright$, leftmargin=20pt, topsep=0pt, itemsep=0pt]
\item Implemented an automated system to optimise communication across the government's analytical units.\\
\end{itemize}
\noindent\colorbox{black}{\parbox{\textwidth}{\color{white}\textbf{\faSeedling\ Recent Achievements}}}

\textbf{Spring 2025:} FSRDC-affiliated data analysis \& visualisation project selected for U.S. Census Bureau presentation.\\
\textbf{Spring 2025:}	Hoenigswald Prize (awarded for a Linguistics thesis w. a significant scientific contribution).\\
\textbf{Spring 2025:} 	Draw Down the Lightning grant of \$8,500 by President J. L. Jameson’s Office (for AI4Good Ideathon).\\
\textbf{Fall 2024: }	Pinkel Fund grant of \$2,000 for experimental research \& Penn Academic Travel Grant.\\
\textbf{Fall 2024: }	Effective Ventures grant of \$5,000 (for AI safety workshop series The New Mind).\\

\noindent\colorbox{black}{\parbox{\textwidth}{\color{white}\textbf{\faLightbulb\ Other Skills}}}
\textbf{Languages:} English (C2) $\bullet$ Czech (C2) $\bullet$ Slovak (C2) $\bullet$ German (rusty) $\bullet$ Polish (rusty) $\bullet$ Python $\bullet$ Java

\textbf{Tech:} MS Office $\bullet$ \LaTeX\ $\bullet$ (some) web design (JS React, HTML, CSS) $\bullet$ data analytics (SQL, BigQuery)

\textbf{Interests:} Games (detective stories, sci-fi) $\bullet$ Languages $\bullet$ Late-Night Chats $\bullet$ Creative Writing

\textbf{Volunteering:} ESPR (Jr Counsellor, 2022); SPARC (Jr Counsellor, 2022; 2025)


\end{document}
